Measuring Subgroup Preferences in Conjoint Experiments

### 2018-11-03 manuscript.tex
add edits from James (2018-10-29)

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## R version 3.5.1 (2018-07-02)
## Platform: x86_64-w64-mingw32/x64 (64-bit)
## Running under: Windows 7 x64 (build 7601) Service Pack 1
## 
## Matrix products: default
## 
## locale:
## [1] LC_COLLATE=English_United Kingdom.1252 
## [2] LC_CTYPE=English_United Kingdom.1252   
## [3] LC_MONETARY=English_United Kingdom.1252
## [4] LC_NUMERIC=C                           
## [5] LC_TIME=English_United Kingdom.1252    
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] ggplot2_3.0.0 cregg_0.2.3   rio_0.5.11   
## 
## loaded via a namespace (and not attached):
##  [1] zip_1.0.0         Rcpp_0.12.17      cellranger_1.1.0 
##  [4] pillar_1.2.3      compiler_3.5.1    plyr_1.8.4       
##  [7] bindr_0.1.1       forcats_0.3.0     tools_3.5.1      
## [10] digest_0.6.15     lattice_0.20-35   ggstance_0.3     
## [13] evaluate_0.10.1   tibble_1.4.2      gtable_0.2.0     
## [16] pkgconfig_2.0.1   rlang_0.2.1       Matrix_1.2-14    
## [19] openxlsx_4.1.0    curl_3.2          haven_1.1.2      
## [22] bindrcpp_0.2.2    withr_2.1.2       stringr_1.3.1    
## [25] dplyr_0.7.6       knitr_1.20        hms_0.4.2        
## [28] lmtest_0.9-36     grid_3.5.1        tidyselect_0.2.4 
## [31] glue_1.2.0        data.table_1.11.4 R6_2.2.2         
## [34] survival_2.42-4   readxl_1.1.0      foreign_0.8-70   
## [37] reshape2_1.4.3    readr_1.1.1       purrr_0.2.5      
## [40] magrittr_1.5      codetools_0.2-15  splines_3.5.1    
## [43] scales_0.5.0      assertthat_0.2.0  xtable_1.8-2     
## [46] colorspace_1.3-2  labeling_0.3      sandwich_2.4-0   
## [49] survey_3.33-2     stringi_1.1.7     lazyeval_0.2.1   
## [52] munsell_0.5.0     zoo_1.8-2
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## R version 3.5.1 (2018-07-02)
## Platform: x86_64-w64-mingw32/x64 (64-bit)
## Running under: Windows 7 x64 (build 7601) Service Pack 1
## 
## Matrix products: default
## 
## locale:
## [1] LC_COLLATE=English_United Kingdom.1252 
## [2] LC_CTYPE=English_United Kingdom.1252   
## [3] LC_MONETARY=English_United Kingdom.1252
## [4] LC_NUMERIC=C                           
## [5] LC_TIME=English_United Kingdom.1252    
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] ggplot2_3.0.0 cregg_0.3.0   rio_0.5.11   
## 
## loaded via a namespace (and not attached):
##  [1] zip_1.0.0         Rcpp_0.12.18      cellranger_1.1.0 
##  [4] pillar_1.3.0.9000 compiler_3.5.1    plyr_1.8.4       
##  [7] bindr_0.1.1       forcats_0.3.0     tools_3.5.1      
## [10] digest_0.6.16     lattice_0.20-35   ggstance_0.3.1   
## [13] evaluate_0.11     tibble_1.4.2      gtable_0.2.0     
## [16] pkgconfig_2.0.2   rlang_0.2.2       Matrix_1.2-14    
## [19] openxlsx_4.1.0    curl_3.2          haven_1.1.2.9000 
## [22] bindrcpp_0.2.2    withr_2.1.2       stringr_1.3.1    
## [25] dplyr_0.7.6       knitr_1.20        hms_0.4.2        
## [28] lmtest_0.9-36     tidyselect_0.2.4  grid_3.5.1       
## [31] glue_1.3.0        data.table_1.11.4 R6_2.2.2         
## [34] survival_2.42-6   readxl_1.1.0      foreign_0.8-71   
## [37] purrr_0.2.5       magrittr_1.5      splines_3.5.1    
## [40] scales_1.0.0      assertthat_0.2.0  xtable_1.8-2     
## [43] colorspace_1.3-2  sandwich_2.5-0    survey_3.33-2    
## [46] stringi_1.1.7     lazyeval_0.2.1    munsell_0.5.0    
## [49] crayon_1.3.4      zoo_1.8-3
\end{verbatim}
\end{kframe}
\end{knitrout}
